Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-13 crass/crassnew.tex
Adding the choice of shift e for additive approach

Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$. To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ are selected as follows:
\begin{itemize}
\item[i)] at iteration $\ell=0$, vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
\item[ii)] for $\ell \geq1$, we use the following result:
$(B_0,\oplus)$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$. From Lagrange's Theorem, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, $\ve=(\ve_1,\dots,\ve_s) \in \left(\mathbb{F}_2^{r}\right)^{s}$
%, which form a partition of $\left(\mathbb{F}_2^{r}\right)^{s}$
. At iteration $\ell \geq1$, we select $\ve$ such that $B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$, and it will be enough to choose $\ve\notin\mathcal{P}_{\ell-1}$. By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.

>>>>

Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$. To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ are selected as follows:
\begin{itemize}
\item[i)] at iteration $\ell=0$, vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
\item[ii)] for $\ell \geq1$, we use the following result:
$(B_0,\oplus)$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$. From Lagrange's Theorem, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, $\ve=(\ve_1,\dots,\ve_s) \in \left(\mathbb{F}_2^{r}\right)^{s}$
%, which form a partition of $\left(\mathbb{F}_2^{r}\right)^{s}$
. At iteration $\ell \geq1$, we select $\ve$ such that $B_{\ell}=B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$. It will be enough to choose $\ve$ such that $\ve\notin\mathcal{P}_{\ell-1}$. %By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
